MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites

### 2014-08-28 chapters/supplementaryMaterial.tex
current copy.
Added the supplementary  section

\pagebreak
\clearpage
\section{Supplementary Material}
\label{sec:sm}

\begin{figure}
\centering
\subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/glass-scalar.eps}}
  \subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/glass-scalar-slice}}
  \subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/glass-cluster-b.eps}}
  \subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/glass-cluster-a.eps}}
  \caption{Our algorithm on a data set made of glass fibers. (a) The scalar dataset, (b) Depicts a slice from the data set, the  fibers are clearly demarcated from the rest of the matrix as oppose to the type of data  where it is hard to distinguish the fibers (Fig.~\ref{fig:data-char} or Fig.~\ref{fig:prepreg}A). (c) The result of the MetaTracts process, the colors are to help visualization. (d) The result of the orientation based clustering, the two clusters are marked red and yellow.}\label{fig:glass}
\end{figure}
\subsection{Glass Fibers}
One simple way we used to validate the accuracy of shape and size of the extracted MetaTracts, is to run the MetaTract technique on Glass fibers.
Unlike the presented data, in glass the fibers are clearly visible (Fig.~\ref{fig:glass}(a)). We noted that the extracted MetaTracts closely followed the fibers in the data.
\subsection{Voxelization and surface extraction Extended}
The voxelization results and some of the meshes extracted from our second data set (Fig.~\ref{fig:prepreg}) are shown in Fig.~\ref{fig:vox_extended}.
\begin{figure}[h]
\centering

\subfloat[]{\includegraphics[width=0.2\textwidth]{imagesMT2014/crop-6-C2-vol}}
\subfloat[]{\includegraphics[width=0.2\textwidth]{imagesMT2014/mesh_prepreg_A}}
\\
\caption{(a) Voxelization of Fig.~\ref{fig:prepreg}C, (b) Shows some of the extracted meshes.}
\label{fig:vox_extended}
\end{figure}
\subsection{Robustness to parameter changes}
Figure~\ref{fig:radius_3} shows the results of data set in Fig.~\ref{fig:data-char} clustered into 2 orientation cluster, and each orientation further clustered into 15 clusters (instead of 10 in Fig.~\ref{fig:len_dist_crop16}). Fig.~\ref{fig:radius_3}(a) shows the number of tracts, the median, minimum and maximum length of the MetaTracts in orientation cluster Fig.~\ref{fig:orientation_clustering}C.
The ground truth is 5 bundles. The radius of the individual MetaTract has been set to 3. We see that similar to Fig~\ref{fig:len_dist_crop16} the correct bundles are identified even with overestimated `h'. The median lengths of the extracted bundles are also similar. Fig~\ref{fig:radius_3}(c, d) shows the individual orientation bundles and Fig~\ref{fig:radius_3}(b) shows the combined bundles.
\begin{figure}[h]
\centering
\subfloat[]{\includegraphics[width=0.6\textwidth]{imagesMT2014/Graph_crop16_3}}\\
\subfloat[]{\includegraphics[width=0.3\textwidth]{imagesMT2014/crop-16/radius_3_orientC}}\\
\subfloat[]{\includegraphics[width=0.25\textwidth]{imagesMT2014/crop-16/radius_3_orientA}}
\subfloat[]{\includegraphics[width=0.25\textwidth]{imagesMT2014/crop-16/radius_3_orientB}}
\caption{(a) Number of tracts and median, minimum and maximum length of individual MetaTracts in the orientation cluster Fig.~\ref{fig:orientation_clustering}C, clustered into 15 clusters (Fig.~\ref{fig:crop-16-decomp}A top). The unit for length is the grid cube length.(b) shows the combined clusters from both the orientation, (c),(d) show the clustering of each orientation.}
\label{fig:radius_3}
\end{figure}

>>>>

\pagebreak
\clearpage
\section{Supplementary Material}
\label{sec:sm}
 In this section we show the results of some extended tests.
 section~\ref{subsec:glass} shows our results on glass fibers. Section~\ref{subsec:vox_ex} shows the some more results of voxelization and mesh generation. Section~\ref{subsec:compare} shows comparisons to hierarchical clustering and with individual fiber extraction technique. Finally, section~\ref{subsec:robustness} shows another result with different parameter to show robustness of parameter selection.

\begin{figure}
\centering
\subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/glass-scalar.eps}}
  \subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/glass-scalar-slice}}
  \subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/glass-cluster-b.eps}}
  \subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/glass-cluster-a.eps}}
  \caption{Our algorithm on a data set made of glass fibers. (a) The scalar dataset, (b) Depicts a slice from the data set, the  fibers are clearly demarcated from the rest of the matrix as oppose to the type of data  where it is hard to distinguish the fibers (Fig.~\ref{fig:data-char} or Fig.~\ref{fig:prepreg}A). (c) The result of the MetaTracts process, the colors are to help visualization. (d) The result of the orientation based clustering, the two clusters are marked red and yellow.}\label{fig:glass}
\end{figure}
\subsection{Glass Fibers}
\label{subsec:glass}
One simple way we used to validate the accuracy of shape and size of the extracted MetaTracts, is to run the MetaTract technique on Glass fibers.
Unlike the presented data, in glass the fibers are clearly visible (Fig.~\ref{fig:glass}(a)). We noted that the extracted MetaTracts closely followed the fibers in the data.
\subsection{Voxelization and surface extraction Extended}
\label{subsec:vox_ex}
The voxelization results and some of the meshes extracted from our second data set (Fig.~\ref{fig:prepreg}) are shown in Fig.~\ref{fig:vox_extended}.
\begin{figure}[h]
\centering
\subfloat[]{\includegraphics[width=0.2\textwidth]{imagesMT2014/crop-6-C2-vol}}
\subfloat[]{\includegraphics[width=0.2\textwidth]{imagesMT2014/mesh_prepreg_A}}
\\
\caption{(a) Voxelization of Fig.~\ref{fig:prepreg}C, (b) Shows some of the extracted meshes.}
\label{fig:vox_extended}
\end{figure}
\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{imagesMT2014/UserStudy/vol_crop16}
\\
\caption{ A shows the Voxelization of Fig.~\ref{fig:data-char}. B shows a single slice. C the slice of original data. }
\label{fig:vox_extended_crop16}
\end{figure}

\begin{figure}[h]
\centering
\subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/compare-clus-1.eps}}
\subfloat[]{\includegraphics[width=0.33\linewidth]{imagesMT2014/compare-clus-3.png}}
\subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/Fiber_extraction_for_bundles_1.eps}}
\subfloat[]{\includegraphics[width=0.25\linewidth]{imagesMT2014/Fiber_extraction_for_bundles_2.eps}}

   \caption{\textit{Comparison of clustering approaches}.(a)Our approach,  Orientation clustering into 2 classes followed by hierarchical clustering into 3 classes each. (b) Hierarchical clustering into 6 classes based on proximity alone.\\
   \textit{Comparison of fiber extraction approaches}. (c) Salaberger et al. ~\cite{Salaberger2011}, they generate numerous small length fibers and miss the curved bundles. (d) close up of the medial axis generated by their approach.}\label{fig:compare-3}
\end{figure}
\subsection {Comparison with hierarchical fiber clustering}
\label{subsec:compare}
Here we compare our framework against the single link clustering based on proximity alone as used by Zhang et al.\cite{Zhang2008}, Moberts et al.\cite{Moberts2005}. In Fig.~\ref{fig:compare-3}(a) we see the results of our approach. 169 fibers were first clustered based on orientation into 2 clusters and then each cluster was classified into 3 classes. In Fig.~\ref{fig:compare-3}(b) we see the results of direct hierarchical clustering of the distances into 6 classes. Direct hierarchical clustering based on proximity alone is not able to partition well, especially in the presence of partially overlapping tracts (Fig.~\ref{fig:length_distribution}(b)). Without the iterative approach (section~\ref{subsec:dist_clustering}) single linkage clustering tends to produce large clusters( `green' in Fig.~\ref{fig:compare-3}(b)) and outliers as separate cluster. The green cluster incorrectly contains MetaTracts from three different fiber bundles (A,D,B). In our approach all major fiber bundles are classified separately.
\subsection{Comparison with individual fiber extraction method}
 Recently  Salaberger et al.~\cite{Salaberger2011} provided a method to study the fiber length distribution in XCT data by extracting individual fibers. They employ the Hessian followed by a medial axis detection approach to follow  individual fibers. We apply their algorithm to show the short comings of applying current fiber detection approaches on our datasets. Fig.~\ref{fig:compare-3}(c-d) shows the comparison between our approaches. Fig.~\ref{fig:compare-3}(c) shows the medial axis extracted by their algorithm. Fig.~\ref{fig:compare-3}(d) shows a close up view. The width of the line is not important because cylinders could be drawn around (c) to produce the same effect as MetaTracts. Their ~\cite{Salaberger2011} approach is designed for well separated fibers, so in our data it produces numerous small length fibers, more over due to the high noise in the Hessians around the curved bundles and the lack of well separated fibers, their approach completely misses the curved bundle.

\subsection{Robustness to parameter changes}
\label{subsec:robustness}
Figure~\ref{fig:radius_3} shows the results of data set in Fig.~\ref{fig:data-char} clustered into 2 orientation cluster, and each orientation further clustered into 15 clusters (instead of 10 in Fig.~\ref{fig:len_dist_crop16}). Fig.~\ref{fig:radius_3}(a) shows the number of tracts, the median, minimum and maximum length of the MetaTracts in orientation cluster Fig.~\ref{fig:orientation_clustering}C.
The ground truth is 5 bundles. The radius of the individual MetaTract has been set to 3. We see that similar to Fig~\ref{fig:len_dist_crop16} the correct bundles are identified even with overestimated `h'. The median lengths of the extracted bundles are also similar. Fig~\ref{fig:radius_3}(c, d) shows the individual orientation bundles and Fig~\ref{fig:radius_3}(b) shows the combined bundles.
\begin{figure*}
\centering
\subfloat[]{\includegraphics[width=0.6\textwidth]{imagesMT2014/Graph_crop16_3}}\\
\subfloat[]{\includegraphics[width=0.3\textwidth]{imagesMT2014/crop-16/radius_3_orientC}}
\subfloat[]{\includegraphics[width=0.25\textwidth]{imagesMT2014/crop-16/radius_3_orientA}}
\subfloat[]{\includegraphics[width=0.25\textwidth]{imagesMT2014/crop-16/radius_3_orientB}}
\caption{(a) Number of tracts and median, minimum and maximum length of individual MetaTracts in the orientation cluster Fig.~\ref{fig:orientation_clustering}C, clustered into 15 clusters (Fig.~\ref{fig:crop-16-decomp}A top). The unit for length is the grid cube length.(b) shows the combined clusters from both the orientation, (c),(d) show the clustering of each orientation.}
\label{fig:radius_3}
\end{figure*}

### 2014-08-28 metaTracts-pvis2014.tex
updated copy added a section
Added the supplementary  section

%% Abstract section.
\abstract{
Carbon fiber reinforced polymers are bundles of individual carbon fibers woven into sheets of carbon fiber cloth which are layered
and reinforced by an epoxy material. Industrial 3D X-ray computed tomography (XCT) generates a 3D volumetric representation of a scanned object, reconstructed from a series of 2D penetration images,
taken throughout a full rotation of the object.	We describe a technique for extracting and visualizing fiber bundles in fiber reinforced composites scanned with X-ray computed tomography.
Our goal is to visualize the geometric structures of the weaving pattern by analyzing large  areas of  composite woven fabrics using XCT scans of low resolution. Individual fibers are barely visible in such scans. We apply and extend methods originally developed for diffusion tensor imaging (DTI) on the generated XCT data. In the first step a coarse version of integral curves is used to extract sections of the fiber bundles in the woven fabrics. We call these sections MetaTracts.
In the next step the extracted fiber bundle sections are clustered using a two phase approach, wherein we first cluster according to orientation and then  cluster by proximity. We test our algorithm on a number of data sets and show that it effectively identifies and separates different fiber bundles. This work will provide a stepping stone to introduce novel non destructive testing techniques for reinforced fiber bundles analysis.
} % end of abstract

@@

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{xBundle}
\end{document}

>>>>

%% Abstract section.
\abstract{
Carbon fiber reinforced polymers are bundles of individual carbon fibers (henceforth referred to as fiber bundle) woven into sheets of carbon fiber cloth which are layered
and reinforced by an epoxy material. Industrial 3D X-ray computed tomography (XCT) generates a 3D volumetric representation of a scanned object, reconstructed from a series of 2D penetration images,
taken throughout a full rotation of the object.	We describe a technique for extracting and visualizing fiber bundles in fiber reinforced composites scanned with X-ray computed tomography. Current approaches focus on identifying and extracting individual fibers.
Our goal is to visualize the geometric structures of the weaving pattern by analyzing large  areas of  composite woven fabrics using XCT scans of low resolution. Individual fibers are barely visible in such scans. We apply and extend methods originally developed for diffusion tensor imaging (DTI) on the generated XCT data. In the first step a coarse version of integral curves is used to extract sections of the fiber bundles in the woven fabrics. We call these sections MetaTracts.
Next the extracted fiber bundle sections are clustered using a two step approach, wherein we first cluster according to orientation and then  cluster by proximity. We test our algorithm on a number of data sets and show that it effectively identifies and separates different fiber bundles. This work will provide a stepping stone to introduce novel non destructive testing techniques for reinforced fiber bundles analysis.
} % end of abstract

@@

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{xBundle}
\input {./chapters/supplementaryMaterial.tex}
\end{document}
